A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-08-25 none_feedback_sequence_classifier/doc/main.tex
update figures

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{mathrsfs}
\usepackage{algpseudocode}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

@@

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
A {\it sequence-to-sequence}
speech recognizers maps a sequence of input acoustic features into a sequence 
of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
Mathematically, this model is 
represented by the following transformation $\mathcal{T}$ 
\cite{a_graves_icml_2006_00}:
\begin{align}
  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
	\label{eq:transformation}
\end{align}
where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
labels, which may be graphemes 
\cite{j_chorowski_nips_2015_00,
w_chan_icassp_2016_00},
subword units \cite{
a_zeyer_interspeech_2018_00,
c_chiu_icassp_2018_00},
 and words \cite{h_soltau_interspeech_2017_00}.
Let us denote a sequence of input acoustic feature vectors by 
$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
{\it one-hot vector} representation or its label-smoothed 
representation \cite{} by 
$\mathcal{Y}_{0}^{L-1}$ as shown below:
\begin{subequations}
  \begin{align}
    \mathcal{X}[0:M]  =  
      \left\{\vec{x}[m]
          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
    \label{eq:input_seq} \\
    \mathcal{Y}_{0:L}  =  
      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
    \label{eq:target_label}
  \end{align}
\end{subequations}
where $M$ is the number of frames in the input feature sequence,
$L$ is the number of labels in the output target sequence,
 and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
Note that the sequence index in \eqref{eq:input_seq} is a frame
index ({\it represented by} [m]), 
whereas the sequence index in \eqref{eq:target_label} is 
a label index ({\it represented by a subscript} $l$). 
Depending on whether the neural network generates
the inference output for every frame or not, there are following
categories:

\subsection{Label-synchronous inference}
In this class of models, the neural network generates the inference output 
$\widehat{\vec{y_l}}$ 
only when a new label is expected. The loss function 
$\mathbb{L}_{\text{ls}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
defined as follows:
   \begin{align}
     \mathbb{L}_{\text{ls}}\left(\mathcal{X}[0:M], 
        \mathcal{Y}_{0:L}\right) 
        = \sum_{l=0}^{L-1} 
          \sum_{v=0}^{V-1}
          \left(\vec{y}_l\right)_v  \log ( 
             \widehat{\vec{y_l}} )_{v}
          \label{eq:label_synchronous_ce_loss} 
   \end{align}
where $V$ is the number of output labels in the set $\mathbb{V}$ 
mentioned in \eqref{eq:target_label}, and ${(\vec{y}_l)}_v$  
and ${(\widehat{\vec{y_l}})}_{v}$ are the $v$-th element of the 
ground-truth vector $\vec{y}_l$ and the estimated vector by the 
neural network ${\widehat{\vec{y_l}}}$.

@@

Using these alignment algorithms, 
we obtain corresponding {\it frame-synchronous} label sequences 
$\vec{z}[m] \in \mathbb{V}$ for each frame index $m$. This
latent label sequences are often called a {\it path}.
  \begin{align}
    \mathcal{Z}[0:M]  =  
      \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
    \label{eq:latent_label_seq}
  \end{align}
Fig. \ref{fig:path_alignment} shows one such example.

The loss function in the frame-synchronous inference case
$\mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
defined as follows:
\begin{align}
  \mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Z}[0:M]\right) 
      = \sum_{l=0}^{M-1} 
          \sum_{v=0}^{V-1}  
            (\vec{z}[m])_v  
            \log (\widehat{\vec{z}}[m])_v  
        \label{eq:frame_synchronous_ce_loss} 
\end{align}

@@

Fig. \ref{fig:ctc_diagram} shows the entire structure of the 
Connectionist Temporal Classification (CTC) 
\cite{a_graves_icml_2006_00}. In CTC, we use the following CTC loss
\cite{a_graves_icml_2006_00, y_he_icassp_2019_00}:
\begin{align}
  P\left(\mathcal{Y}_{0:L} | \mathcal{X}[0:M]\right) = 
    \sum_{\mathcal{Z}_{0}^{M-1} \in 
      \mathcal{A}_{CTC} 
        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
          \Pi_{m=0}^{M-1}
            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
\end{align}
where $\mathcal{A}_{CTC} \left(\mathcal{X}_{0}^{M-1}, 
\mathcal{Y}_{0}^{L-1} \right)$ correspond to frame-level alignments
of length $M$ such that removing blanks and repeated symbols from 
$\mathcal{Z}_{0}^{M-1}$ yields $\mathcal{Y}_{0}^{L-1}$.

@@

Fig. \ref{fig:rnn_t_diagram} shows the entire structure of the  
RNN-T structure. The loss function used in RNN-T is given as follows:
\begin{align}
  P\left(\mathcal{Y}_{0:L} | \mathcal{X}[0:M]\right) = 
    \sum_{\mathcal{Z}_{0}^{M-1} \in 
      \mathcal{A}_{CTC} 
        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
          \Pi_{m=0}^{M-1}
            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
\end{align}

@@

@@

FSC performs inference in a frame-synchronous way as described in 
Sec. \ref{sec:frame_synchronous_inference}. 
However, due to this temporal sub-sampling, the latent label sequence 
in \eqref{eq:latent_label_seq} is slightly modified as shown below:
\begin{align}
  \mathcal{Z}[0:U]  =  
    \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
  \label{eq:subsampled_latent_label_seq}
\end{align}

The loss function 
$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ 
is also modified from the original one in 
\eqref{eq:frame_synchronous_ce_loss}:
\begin{align}
	\mathbb{L}_{\text{fsc}}
    \left(\mathcal{X}[0:M], \mathcal{Z}_{0:U}\right)
      = \sum_{u=0}^{U-1}  
          \sum_{v=0}^{V-1}
          {(\vec{z}[u])_v}  \log ( 
             \widehat{\vec{z}}[u] )_v  
        \label{eq:fsc_ce_loss} 
\end{align}
The reason for performing the 8:1 temporal sub-sampling in \eqref{eq:def_u_U} is to 
to make the period of the softmax output $\widehat{\vec{z}}[u]$ in \label{eq:fsc_ce_loss} 
be similar to the shortest BPE duration. We assume that the {\it sequence-to-sequence}
neural network models will be trained most efficiently when the period of neural 
network output roughly matches the period of the target. In addition, this
output periods must be equal to larger than the shortest target period to prevent
missing some targets.
The shortest duration of each BPE is similar to the average length of {\it phones}, 
which is any distinct speech sound serving as a phonetic unit.
It has been observed that the average phone duration is between 50 {\it ms}
\textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.
Under this rationale, we chose the temporal sub-sampling factor of 8:1. 
We also observe this sub-sampling factor is optimal in our experiments as well.

@@

When creating the latent frame-wise label sequence $\mathcal{Z}[0:U]$ 
in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
from other frames.  For example, if we have a BPE unit
("{\it an}") in the vocabulary $\mathbb{V}$, then we define another
target ("{\it an$_o$}") which marks the on-set frame of this BPE
interval. Thus, when the number of BPE units is $B$, the total
number of vocabularies in $\mathbb{V}$ becomes $2B$.
We refer this approach to as {\it BPE with onset marking}.

@@

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}[0:M]$.

\begin{algorithm}
  \caption{Training procedure for the FSC algorithm}
  \label{algo:fsc_training}
  \begin{algorithmic}
    \State $\Theta^{(0)} \leftarrow$ initialize\_parameters()
    \For {epoch index $i = 0, . . . , I-1$}
      \For {each batch $\left\{\mathcal{X}[0:M],
                        \mathcal{Y}_{0:L}  \right\}$}, 
        \State $ {{\mathcal{Z}^{(i)}}[0:U]}
          \leftarrow
          \text{n\_best\_align}
          \left(
            \mathcal{X}[0:M] \Big| \Theta^{(i)}
          \right)$

        \State {$\Theta^{(i)} \leftarrow$ update\_parameter 
          $\left(
            \mathcal{X}[0:M],
            \mathcal{Z}^{(i)}[0:U]
          \right)$}

@@

\begin{figure}
  \centering
    \resizebox{100mm}{!}{
      \input{../figures/path_alignment.tex}
    } 
    \caption {
      An example of a path $\mathcal{Z}[0:M]$ and the path movement 
      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
      \label{fig:path_alignment}
    }
  \label{fig:path_alignment}
\end{figure}

@@

\begin{algorithm}
  \caption{$N$-best alignment algorithm}
  \begin{algorithmic}

  \Require {$\mathcal{X}[0:M]$}
  \Require {$\mathcal{Y}_{0:L}$}
  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
    for calculating 
      $p\left(\vec{z}[m] \big|
      \mathcal{Z}[0:m], \mathcal{X}[0:m+1]\right)$}

  \State {\textbf{Initialization:}}
  \State {Let $\mathcal{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
  \State {Let $\mathcal{L}_{0} := \ln \left[ 
        p \left(\vec{y}_{0} \big| 
            {\mathcal{X}}[0:1]\right)  \right]$}
  \State {$\mathcal{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
  \For {$m = 1, . . . , M-1$}
    \For {$b = 0, . . . , N_b-1$}
      \If {$\mathcal{Z}_{b}[0:m]$ is defined}
        \State {Let $\vec{y}_u := \vec{z}_{b}[m-1] $}
        \State {Let $\mathcal{Z}_{b, 0}[0:m+1] := \mathcal{Z}_{b}[0:m] 
                \cup \left\{ \vec{y}_u  \right\}  $} 
            \Comment {A horizontal move $P \rightarrow Q$ in 
            Fig. \ref{fig:path_alignment}}.
        \State {
              $\mathcal{L}_{b,0} := \ln \left[ 
                  p \left(\vec{y}_{u} \big| 
                      \mathcal{Z}_b[0:m], 
                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right]
                  + \mathcal{L}_b$}

        \If {$u+1 \le  L - 1$}
          \State {Let $\mathcal{Z}_{b, 1}[0:m+1] 
          := {\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
          \State  {
              $\mathcal{L}_{b,1} := \ln \left[ 
                  p \left(\vec{y}_{u+1} \big| 
                      \mathcal{Z}_b[0:m], 
                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right] 
                          + \mathcal{L}_b$}
      \EndIf
      \EndIf
    \EndFor
    \State {Sort a list of items
    $\left\{\mathcal{L}_{b, i}, {\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le
    b < N_b, i = 0, 1$ 
    with respect to the log likelihood $\mathcal{L}_{b, i}$ 
    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
    follows: 
    $\left\{\mathcal{L}_{b}, \mathcal{Z}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
    where the first item in the sorted list is re-indexed to $b=0$, 
    the second item is re-indexed to $b=1$, and so on.
  \EndFor
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{mathrsfs}
\usepackage{algpseudocode}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usepackage[cal=boondox,scr=boondoxo]{mathalfa}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

@@

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
A {\it sequence-to-sequence}
speech recognizers maps a sequence of input acoustic features into a sequence 
of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
Mathematically, this model is 
represented by the following transformation $\mathcal{T}$ 
\cite{a_graves_icml_2006_00}:
\begin{align}
  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
	\label{eq:transformation}
\end{align}
where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
labels, which may be graphemes 
\cite{j_chorowski_nips_2015_00,
w_chan_icassp_2016_00},
subword units \cite{
a_zeyer_interspeech_2018_00,
c_chiu_icassp_2018_00},
 and words \cite{h_soltau_interspeech_2017_00}.
Let us denote a sequence of input acoustic feature vectors by 
$\vec{x}_{0}^{M-1}$ and a sequence of target labels in 
{\it one-hot vector} representation or its label-smoothed 
representation \cite{} by 
$\vec{y}_{0:L}$ as shown below:
\begin{subequations}
  \begin{align}
    \vec{x}[0:M]  =  
      \left\{\vec{x}[m]
          \, \big| \, 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
    \label{eq:input_seq} \\
    \vec{y}_{0:L}  =  
      \left\{\vec{y}_l \,  \big| \, 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
    \label{eq:target_label}
  \end{align}
\end{subequations}
where $M$ is the number of frames in the input feature sequence,
$L$ is the number of labels in the output target sequence,
 and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
Note that the sequence index in \eqref{eq:input_seq} is a frame
index ({\it represented by} [m]), 
whereas the sequence index in \eqref{eq:target_label} is 
a label index ({\it represented by a subscript} $l$). 
Depending on whether the neural network generates
the inference output for every frame or not, there are following
categories:

\subsection{Label-synchronous inference}
In this class of models, the neural network generates the inference output 
$\widehat{\vec{y_l}}$ 
only when a new label is expected. The loss function 
$\mathbb{L}_{\text{ls}}\left(\vec{x}[0:M], \vec{y}_{0:L}\right)$ is 
defined as follows:
   \begin{align}
     \mathcal{l}_{\text{ls}}\left(\vec{x}[0:M], 
        \vec{y}_{0:L}\right) 
        = \sum_{l=0}^{L-1} 
          \sum_{v=0}^{V-1}
          \left(\vec{y}_l\right)_v  \log ( 
             \widehat{\vec{y_l}} )_{v}
          \label{eq:label_synchronous_ce_loss} 
   \end{align}
where $V$ is the number of output labels in the set $\mathbb{V}$ 
mentioned in \eqref{eq:target_label}, and ${(\vec{y}_l)}_v$  
and ${(\widehat{\vec{y_l}})}_{v}$ are the $v$-th element of the 
ground-truth vector $\vec{y}_l$ and the estimated vector by the 
neural network ${\widehat{\vec{y_l}}}$.

@@

Using these alignment algorithms, 
we obtain corresponding {\it frame-synchronous} label sequences 
$\vec{z}[m] \in \mathbb{V}$ for each frame index $m$. This
latent label sequences are often called a {\it path}.
  \begin{align}
    \vec{z}[0:m+1]  =  
      \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
    \label{eq:latent_label_seq}
  \end{align}
Fig. \ref{fig:path_alignment} shows one such example.

The loss function in the frame-synchronous inference case
$\mathbb{l}_{\text{fs}}\left(\vec{x}[0:M], \vec{y}_{0:L}\right)$ is 
defined as follows:
\begin{align}
  \mathcal{l}_{\text{fs}}\left(x[0:M], z[0:M]\right) 
      = - \sum_{l=0}^{M-1} 
          \sum_{v=0}^{V-1}  
            (\vec{z}[m])_v  \log (\widehat{\vec{z}}[m])_v  
        \label{eq:frame_synchronous_ce_loss} 
\end{align}

@@

Fig. \ref{fig:ctc_diagram} shows the entire structure of the 
Connectionist Temporal Classification (CTC) 
\cite{a_graves_icml_2006_00}. In CTC, we use the following CTC loss
\cite{a_graves_icml_2006_00, y_he_icassp_2019_00}:
\begin{align}
  P\left(\vec{y}_{0:L+1} | \vec{x}[0:M]\right) = 
    \sum_{\vec{z}_{0}^{M-1} \in 
      \mathcal{A}_{CTC} 
        \left(\vec{x}_{0}^{M-1}, \vec{y}_{0}^{L-1} \right)}
          \Pi_{m=0}^{M-1}
            P\left(\vec{z}[m] | \vec{x}_{0}^{M-1} \right),
\end{align}
where $\mathcal{A}_{CTC} \left(\vec{x}_{0}^{M-1}, 
\vec{y}_{0}^{L-1} \right)$ correspond to frame-level alignments
of length $M$ such that removing blanks and repeated symbols from 
$\vec{z}_{0}^{M-1}$ yields $\vec{y}_{0}^{L-1}$.

@@

Fig. \ref{fig:rnn_t_diagram} shows the entire structure of the  
RNN-T structure. The loss function used in RNN-T is given as follows:
\begin{align}
  P\left(\vec{y}_{0:L} | \vec{x}[0:M]\right) = 
    \sum_{\vec{z}_{0}^{M-1} \in 
      \mathcal{A}_{CTC} 
        \left(\vec{x}_{0}^{M-1}, \vec{y}_{0}^{L-1} \right)}
          \Pi_{m=0}^{M-1}
            P\left(\vec{z}[m] | \vec{x}_{0}^{M-1} \right),
\end{align}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \resizebox{50mm}{!}{
      \input{../figures/structure_for_inference.tex}
    } 
  \caption {
    \label{fig:structure_for_inference}
  } 
  \end{subfigure}
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \resizebox{43mm}{!}{
      \input{../figures/structure_for_training.tex}
    } 
  \caption {
    \label{fig:structure_for_training}
  }
  \end{subfigure}
  \caption{
    Structures of sequential hypothesis classifier for inference (a) 
    and for training (b).
  }

@@

FSC performs inference in a frame-synchronous way as described in 
Sec. \ref{sec:frame_synchronous_inference}. 
However, due to this temporal sub-sampling, the latent label sequence 
in \eqref{eq:latent_label_seq} is slightly modified as shown below:
\begin{align}
  \vec{z}[0:U]  =  
    \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
  \label{eq:subsampled_latent_label_seq}
\end{align}

The loss function 
$\mathbb{L}_{\text{fsc}}\left(\vec{x}[0:M], \vec{y}_{0:L}\right)$ 
is also modified from the original one in 
\eqref{eq:frame_synchronous_ce_loss}:
\begin{align}
	\mathbb{L}_{\text{fsc}}
    \left(\vec{x}[0:M], \vec{z}_{0:U}\right)
      = \sum_{u=0}^{U-1}  
          \sum_{v=0}^{V-1}
          {(\vec{z}[u])_v}  \log ( 
             \widehat{\vec{z}}[u] )_v  
        \label{eq:fsc_ce_loss} 
\end{align}
The reason for performing the 8:1 temporal sub-sampling in \eqref{eq:def_u_U} is to 
to make the period of the softmax output $\widehat{\vec{z}}[u]$ in \label{eq:fsc_ce_loss} 
be similar to the shortest BPE duration. We assume that the {\it sequence-to-sequence}
neural network models will be trained most efficiently when the period of neural 
network output roughly matches the period of the target. In addition, this
output periods must be equal to larger than the shortest target period to prevent
missing some targets.
The shortest duration of each BPE is similar to the average length of {\it phones}, 
which is any distinct speech sound serving as a phonetic unit.
It has been observed that the average phone duration is between 50 {\it ms}
\textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.
Under this rationale, we chose the temporal sub-sampling factor of 8:1. 
We also observe this sub-sampling factor is optimal in our experiments as well.

@@

When creating the latent frame-wise label sequence $\vec{z}[0:U]$ 
in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
from other frames.  For example, if we have a BPE unit
("{\it an}") in the vocabulary $\mathbb{V}$, then we define another
target ("{\it an$_o$}") which marks the on-set frame of this BPE
interval. Thus, when the number of BPE units is $B$, the total
number of vocabularies in $\mathbb{V}$ becomes $2B$.
We refer this approach to as {\it BPE with onset marking}.

@@

The first step is finding the optimal frame-synchronous sequence
$\vec{z}[0:M]$.

\begin{algorithm}
  \caption{Training procedure for the FSC algorithm}
  \label{algo:fsc_training}
  \begin{algorithmic}
    \State $\Theta^{(0)} \leftarrow$ \texttt{initialize\_parameters}()
    \For {epoch index $i = 0, . . . , I-1$}
      \For { \texttt{example} $ \left\{\vec{x}[0:M],  \,
                        \vec{y}_{0:L}  \right\} $} 
        \State $ {\vec{z}^{(i)}}[0:U] 
          \leftarrow
          \texttt{n\_best\_align}
          \left(
            \vec{x}[0:M] \, \big|\, \Theta^{(i)}
          \right)$

        \State {$\Theta^{(i)} \leftarrow$  \texttt {update\_parameter}
          $\left(
            \vec{x}[0:M] \, ,  \,
            \vec{z}^{(i)}[0:U]
          \right)$}

@@

\begin{figure}
  \centering
    \resizebox{100mm}{!}{
      \input{../figures/path_alignment.tex}
    } 
    \caption {
      An example of the path function $\vec{z}[0:M]$ and the path movement 
      constraint represented by two dashed arrows 
      $P \rightarrow Q$ and $P \rightarrow R$.  \label{fig:path_alignment}
    }
  \label{fig:path_alignment}
\end{figure}

@@

\begin{algorithm}
  \caption{Teacher forced alignment}
  \begin{algorithmic}

  \Require {$\vec{x}[0:M]$}
  \Require {$\vec{y}_{0:L}$}
  \Require {The beam size $N_b$}
  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
    for calculating $\vec{z}[u] = f(\vec{x}[0:m+1],\,z[0:u])$}

  \State {\textbf{Initialization:}}
  \State {Let $z_0[0:1] := \left( \vec{y}_0 \right)  $}
  \State {$z_b[0:1], 1 \le b < N_b$ are undefined.}
  \State {Let $\mathcal{l}_{0} := \ln \left[ 
        p \left(\vec{y}_{0} \, \big|  \,
            {\vec{x}}[0:1]\right)  \right]$}
  \For {$m = 1, . . . , M-1$}
    \For {$b = 0, . . . , N_b-1$}
      \If {$z_{b}[0:m]$ is defined}
        \State {Let $\vec{y}_u := z_{b}[m-1] $}
        \State {Let $z_{b, 0}[0:m+1] := z_{b}[0:m] 
                \frown \left\{ \vec{y}_u  \right\}  $} 
            \Comment {A horizontal move $P \rightarrow Q$ in 
            Fig. \ref{fig:path_alignment}}.
        \State {
              $\mathcal{l}_{b,0} := \ln \left[ 
                  p \left(\vec{y}_{u} \big| 
                      z_b[0:m], 
                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right]
                  + \mathcal{l}_b$}

        \If {$u+1 \le  L - 1$}
          \State {Let $z_{b, 1}[0:m+1] 
          := z_{b}[0:m] \frown \left\{ \vec{y}_{u+1}  \right\}  $} 
              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
          \State  {
              $\mathcal{l}_{b,1} := \ln \left[ 
                  p \left(\vec{y}_{u+1} \big| 
                      z_b[0:m], 
                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right] 
                          + \mathcal{l}_b$}
      \EndIf
      \EndIf
    \EndFor
    \State {Sort a list of items
    $\left\{\mathcal{l}_{b, i}, z_{b, i}[0:m+1] \right\}, \; 0 \le
    b < N_b, i = 0, 1$ 
    with respect to the log likelihood $\mathcal{l}_{b, i}$ 
    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
    follows: 
    $\left\{\mathcal{l}_{b}, z_{b}[0:M] \right\}$, $0 \le b < N_b$}
    where the first item in the sorted list is re-indexed to $b=0$, 
    the second item is re-indexed to $b=1$, and so on.
  \EndFor
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}
